% =====================================================================
%  A Multiverse of Love
%  The Interstellar Psychology Worldview.
%  A stand-alone essay. The procedural infrastructure that operationalises
%  the consensus epistemology argued here is described in two companion
%  papers, referenced once and not relied upon.
%  Author : Neo
%  Class  : article
% =====================================================================

\documentclass[11pt,a4paper]{article}

% ---------- Packages ----------
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{microtype}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}
\usepackage[skins,breakable]{tcolorbox}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[hidelinks,colorlinks=true,linkcolor=black,urlcolor=blue!55!black,citecolor=black]{hyperref}
\usepackage{fancyhdr}

% ---------- Colours ----------
\definecolor{ink}{HTML}{0E1116}
\definecolor{inkfaint}{HTML}{555B66}
\definecolor{accent}{HTML}{6A4CFF}
\definecolor{accent2}{HTML}{1F8F66}
\definecolor{warn}{HTML}{B85C00}
\definecolor{rule}{HTML}{C8CCD3}
\definecolor{panelbg}{HTML}{F6F4EE}

% ---------- Page style ----------
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\footnotesize\textsc{Interstellar Psychology}}
\fancyhead[R]{\footnotesize\textsc{A Multiverse of Love --- a worldview essay}}
\fancyfoot[C]{\footnotesize\thepage}
\renewcommand{\headrulewidth}{0.3pt}
\renewcommand{\footrulewidth}{0pt}

% ---------- Section style ----------
\titleformat{\section}
  {\normalfont\Large\bfseries\color{ink}}
  {\thesection}{0.6em}{}
\titleformat{\subsection}
  {\normalfont\large\bfseries\color{ink}}
  {\thesubsection}{0.6em}{}

% ---------- Helper boxes ----------
\newtcolorbox{plainbox}[1][]{
  enhanced, breakable, boxrule=0pt, frame hidden,
  colback=panelbg, colupper=ink,
  left=10pt, right=10pt, top=8pt, bottom=8pt,
  arc=2pt, #1
}

\newtcolorbox{notebox}[1][]{
  enhanced, breakable, boxrule=0pt, frame hidden,
  colback=panelbg, colupper=ink,
  left=12pt, right=12pt, top=8pt, bottom=8pt,
  borderline west={2pt}{0pt}{accent},
  arc=0pt, #1
}

% ---------- Title block ----------
\title{
  \vspace{-2em}
  {\Huge\bfseries A Multiverse of Love}\\[0.6em]
  {\Large The Interstellar Psychology Worldview}
}
\author{
  \textbf{Neo}\\[0.3em]
  \textit{Interstellar Psychology}
}
\date{May 18, 2026}

% =====================================================================
\begin{document}
% =====================================================================
\maketitle
\thispagestyle{empty}

\vspace{-1em}
\begin{plainbox}
\textbf{Abstract.}
This is a worldview essay. It argues a position rather than verifying
one. The position has two parts. The first is epistemic: knowledge
about contested aspects of reality is not produced by individual
insight or by editorial gatekeeping, but by a revisable consensus
formed in public among accountable peers. The second is metaphysical:
when the available evidence across nine research themes is taken on
its own terms, the most economical reading is that consciousness is
fundamental rather than incidental, that the universe is relational,
and that the relational substrate is what older traditions have
called \emph{love}. The two parts are linked: a consensus-based
epistemology is the only one under which the relevant evidence can
be examined honestly, because mainstream peer review is structurally
unable to host evidence that contradicts its prior ontology. The
essay sets out the nine themes, names the structural reasons the
mainstream cannot adjudicate them, defends the metaphysical reading
against its strongest counter-arguments, and concludes by pointing
--- once --- at the two companion papers in which the consensus
infrastructure is engineered. The essay does not require those
papers. They are described for completeness, not for support.
\end{plainbox}

\tableofcontents
\vspace{1em}
\hrule
\vspace{1em}

% =====================================================================
\section{A Worldview Essay, Not a Proof}
% =====================================================================

This essay sits in a particular epistemic register and it is
important to name it. It is not a scientific paper. It does not
claim that the position it argues is established. It claims that
the position is \emph{worth taking seriously} --- worth holding as
a working hypothesis, worth investigating with the same rigour we
extend to less contested questions, and worth giving an
infrastructure under which it can be examined in public.

The essay does two things. It argues a worldview, and it argues the
epistemology under which a worldview of this kind can be argued in
the first place. The epistemology is load-bearing and deserves its
own statement up front:

\begin{notebox}
\textbf{Truth about contested aspects of reality is not produced by
individual insight or by editorial gatekeeping. It is produced by
a revisable consensus formed in public among accountable peers,
under rules that preserve the dissent. The consensus is provisional;
it can be wrong; it is the best available approximation at a given
moment, and the procedure that produced it must remain open for
later revision.}
\end{notebox}

This is not the only epistemology available. It is the one this
essay defends, because it is the only one under which evidence that
contradicts a prevailing paradigm can be examined honestly --- and
because the same epistemology, extended from contested evidence to
the behaviour of artificial intelligence, gives the only coherent
long-run answer to the question \emph{whose values?}

What follows is what this author personally believes about reality,
the evidence that led him there, and the framing he finds it sits
inside. The companion engineering papers --- one on the alignment
of artificial intelligence, one on the archive infrastructure that
both projects share --- are mentioned once at the end and do not
need to be read for this essay to stand.

% =====================================================================
\section{The Founding Problem}
% =====================================================================

Science advances by a simple loop. Someone proposes a claim, others
examine it, reproduce it, and either accept it into the shared
record or push back against it. The institution we call \emph{peer
review} is the gate that decides what enters that record. It is a
remarkable invention, and over the past three centuries it has
produced most of what we know about the physical world.

It is also a system with two well-known weaknesses.

\begin{enumerate}[leftmargin=1.5em]
  \item \textbf{It is private.} A handful of anonymous reviewers,
        chosen by an editor, decide what is publishable. The
        deliberation is invisible; the criteria are unwritten; the
        rejections do not travel with the paper.
  \item \textbf{It is conservative.} A reviewer who has staked a
        career on one paradigm is the worst possible judge of
        evidence that contradicts it. Topics that fall outside the
        current consensus --- regardless of the quality of the
        data --- are routinely filtered out before publication.
\end{enumerate}

This second weakness is the founding problem of Interstellar
Psychology. A great deal of replicable, recorded, sometimes
\emph{government-declassified} evidence exists for phenomena that
the mainstream is unwilling to host: twenty-three years of CIA
remote-viewing research with quantitative protocols; congressional
testimony on non-human intelligence; controlled trials of
psychedelic therapy with measurable, durable effects on depression
and end-of-life anxiety; on-camera demonstrations of non-speaking
autistic communication observed by multiple independent
investigators; cardiac-arrest survivors describing operating-room
detail consistent with the procedure and the room's layout. The
data is not in dispute. The \emph{venue} is.

What the author has been led to, over the past few years of
working through this material, is the conviction that the missing
venue is the problem. The mainstream is not failing to test these
phenomena because the evidence is poor. It is declining to host
the conversation because the conversation does not fit the
prevailing ontology. A different venue --- public, named,
revisable, tamper-evident --- can host it without asking the
mainstream's permission. That is the practical project. The
worldview that follows is what one comes to believe when one takes
the evidence on its own terms and asks where it points.

% =====================================================================
\section{The Position}
% =====================================================================

The position argued in this essay is a single claim, stated in two
forms.

\begin{notebox}
\textbf{Long form.}
Consciousness is fundamental to reality rather than incidental to
it; the universe is relational, a fabric in which conscious beings
recognise one another; the relational substrate is what older
traditions have called \emph{love}; and the accumulated evidence
for non-local, non-material, and non-coincidental phenomena is best
read as the universe \emph{participating} in the lives of the
conscious beings inside it rather than \emph{containing} them as
inert matter.

\textbf{Short form.} A multiverse of love.
\end{notebox}

This is, deliberately, a metaphysical claim. It is not a scientific
hypothesis in the testable-this-week sense, and we will not pretend
it is. It is a \emph{framing} --- a position about what the
universe is for, under which a great deal of disparate evidence
becomes a single story rather than nine unrelated anomalies. The
essay's job is to make that framing legible enough that a reader
can decide whether to share it. The reader who does not share it
loses nothing; the essay does not stake any other claim on it.

We are not asking the reader to take the worldview on the author's
word. We are asking the reader to consider whether the worldview is
more economical than the alternative, given what is actually in the
record --- and to weigh the strongest counter-arguments, which we
will set out honestly as we go.

% =====================================================================
\section{The Nine Pillars}
% =====================================================================

Interstellar Psychology investigates nine research themes. They are
not the worldview's premises; they are the territories in which the
relevant evidence lives. We are honest in advance about two things.
First, the nine are heterogeneous in evidentiary status: declassified
CIA remote-viewing protocols and an intuitive reading of music as
recognition-across-cultures are not on the same footing, and we will
not pretend otherwise. Second, the partition is the author's current
best cut; future work may merge, split, or replace any of them. The
nine are listed first as a map; the harder cases are then defended
in detail in \S5.

\begin{plainbox}
\begin{tabular}{@{}p{0.4cm} p{4.2cm} p{9cm}@{}}
\textbf{1} & Music                   & Sound as a harmonic substrate in which recognition occurs across cultures and centuries. The weakest pillar evidentially, the most universally felt experientially. Listed because its phenomenology is what the substrate hypothesis would predict, not because it constitutes evidence on its own. \\
\textbf{2} & Psychedelics            & Compounds that reliably reproduce mystical experiences in controlled settings, with measurable durable effects on depression, end-of-life anxiety, and meaning-making. The trial data is published and replicated. \\
\textbf{3} & Telepathy               & Non-speaking autistic individuals demonstrating mind-to-mind communication on camera, repeatedly, with multiple independent investigators present. The Telepathy Tapes is the current standard public record. \\
\textbf{4} & Mindsight               & Children trained to read text and identify colours while fully blindfolded, in publicly demonstrable conditions, across multiple training programmes operating independently. \\
\textbf{5} & Remote Viewing          & Twenty-three years of declassified CIA / DIA research (Stargate and predecessors) into non-local perception, with quantitative protocols, controls, and statistical analyses now in the public record. \\
\textbf{6} & Out-of-Body Experience  & Cardiac-arrest survivors describing operating rooms in detail consistent with the procedure and the room's layout, from a perspective that does not correspond to their physical position. \\
\textbf{7} & Non-Human Intelligence  & From AAWSAP through congressional testimony --- the official question has shifted from whether to what. The record is now substantial enough that any cosmology has to account for it. \\
\textbf{8} & Multiverse              & Synchronicity treated as a class of data: events whose joint occurrence is so unlikely under independence that their persistence across populations is itself the phenomenon. \\
\textbf{9} & Infinity                & Recursive self-similarity in observed natural structures: scale-invariance in cosmological large-scale structure, fractal organisation in coastlines, vasculature, and lung branching, and the recurrence of strange-attractor geometry in dynamical systems. Listed as the geometric signature one would expect of a non-closed, self-referential cosmos rather than as a stand-alone evidentiary pillar. \\
\end{tabular}
\end{plainbox}

The nine pillars are not the claim of the system. They are the
\emph{question}. The claims live inside them.

We are deliberately not making a unified mechanistic argument
linking the nine. Such an argument may eventually exist; the author
suspects it will involve consciousness as a fundamental property
rather than an emergent one, and the universe as a recursive
structure that admits non-local correlation. But the worldview does
not depend on the unified mechanism. It depends on the more modest
claim that, taken together with their respective counter-arguments
handled honestly, these nine bodies of evidence are better explained
by a relational, conscious universe than by a universe in which they
are nine independent statistical flukes.

% =====================================================================
\section{The Strongest Counter-Arguments, Engaged}
\label{sec:counter}
% =====================================================================

A worldview essay that does not engage the standard critiques is
not worth reading. We engage them here.

\paragraph{OBE / cardiac-arrest reports have known confounds.}
The mainstream literature attributes operating-room reports to
residual cortical activity below detection threshold, post-hoc
reconstruction from auditory cues during anaesthesia awareness, and
confabulation under the strong narrative pressure of a near-death
experience. These are real confounds and the strongest cases
control for them imperfectly. The most defensible position is not
that confounds are absent; it is that the better-controlled cases
(Parnia's AWARE studies, Sabom's earlier veridical-perception work)
report detail that is hard to recover from those confounds alone,
and that the dismissive reading requires the confounds to be doing
more work than they plausibly can. We are claiming an unsettled
record, not a settled one. The essay's argument does not need the
record to be settled; it needs the record to be unsettled enough
that mainstream certainty is itself the anomaly.

\paragraph{Remote-viewing statistics regress to chance with
methodology improvements.} The standard critique of Stargate is
that effect sizes shrink as protocols tighten, and that the
remaining signal is consistent with sensory leakage and judging
bias. The fair counter-reading is that effect sizes shrink but do
not vanish, that the surviving signal across two decades of
in-house critics is small but reliably non-zero, and that a
laboratory with this much adversarial scrutiny producing a stable
small effect is closer to a discovery than to a null result. We
acknowledge the effect is small. We deny that small effects of this
kind, replicated under tightening methodology by hostile
reviewers, are nothing.

\paragraph{Telepathy demonstrations rely on facilitator influence.}
The standard critique of non-speaking autistic telepathy is that
the facilitator unconsciously cues the subject (the ideomotor
effect, well-documented for facilitated communication generally).
The strongest investigations specifically address this with
double-blind setups: the facilitator does not know the target, the
target is randomised by an independent party, and the subject
still performs. The work that does \emph{not} control for this is
weak; the work that does is the work we are pointing at. The
critique applies; it does not generalise to the controlled cases.

\paragraph{Psychedelic-trial effects regress under improved
blinding.} The honest version of this concern is that participants
in psychedelic trials cannot be blinded effectively, and the
expectancy effect is doing more work than the molecule. The
counter-evidence is that response durability at six and twelve
months is unusual for an expectancy effect, that
phenomenologically-similar effects appear under blinded conditions
with active placebos in some recent trials, and that the
mechanistic story (serotonergic remodelling, default-mode-network
attenuation) has measurable neural correlates. The effect is real
even if its size has been overstated.

\paragraph{Synchronicity is selection bias.} The standard critique
is that humans notice coincidences and forget non-coincidences, so
the apparent density of synchronicity is an artefact of selective
recall. This is correct as far as it goes. The argument here is
not that any single synchronicity is evidence; it is that the
\emph{class} of events --- treated under proper Bayesian priors,
across populations, with pre-registered targets --- is worth a
venue. The mainstream has no such venue, so the question goes
unanswered. We are claiming the question is worth answering, not
that we have answered it.

\paragraph{Non-human intelligence reports remain unverified at the
physical-evidence level.} Congressional testimony and AAWSAP
documents are testimony, not retrieval. The strongest position is
that the official disclosure has been substantial enough to require
accounting for, that the previous dismissal posture is now
indefensible, and that the next move --- physical evidence,
provenance, materials analysis --- is a research programme rather
than a settled question. We are claiming the question has been
re-opened by the state, not that the state has answered it.

The pattern is the same across the pillars. The strongest
mainstream critiques are real; the strongest data within each
pillar survives them; the aggregate position --- nine independent
research areas with non-trivial signal that the prevailing
ontology cannot host --- is not refuted by any single critique.
A reader who finds two or three pillars unconvincing can still
take the aggregate seriously. A reader who finds all nine
unconvincing is, of course, entitled to that view; the essay's
final move is that even on that reading, a public venue under
which the question can be reopened is worth building.

% =====================================================================
\section{What Mainstream Peer Review Cannot Do}
% =====================================================================

The mainstream's reluctance to host these conversations is not
arbitrary and we do not portray it as such. It has structural
causes worth naming honestly.

\paragraph{Risk asymmetry.} A reviewer who accepts a paper that
turns out to be wrong incurs a much smaller career penalty than a
reviewer who accepts a paper that turns out to be paradigm-shifting
\emph{and} is later attacked by the discipline's defenders. The
incentive is to reject anomalous evidence first and ask questions
later.

\paragraph{Methodological mismatch.} Standard inferential statistics
were designed for repeatable, controlled, mechanism-explained
phenomena. Phenomena that depend on the participation of a
conscious observer --- telepathy, remote viewing, mindsight --- are
not neatly compatible with the assumption that the observer can be
removed from the experiment.

\paragraph{Ontological commitment.} The mainstream operates under a
working assumption that consciousness is an emergent property of
matter. Most of the nine pillars are difficult to read in a way
compatible with that assumption. A reviewer committed to the
assumption can dismiss the evidence without engaging it, because
the evidence cannot fit the prior.

\paragraph{Reputational contamination.} The honest researcher who
works on one of the nine themes becomes hard to cite in adjacent
mainstream literatures, which discourages the careful work and
attracts the careless work. Over time, the field's public surface
is dominated by exactly the contributors a critic would want to
caricature. This is a reputational pump that mainstream peer review
not only fails to correct, but actively produces.

None of these structural causes makes the mainstream wrong about
its own methods. They make the mainstream the wrong venue for the
conversation that is needed. A different venue can address the
methodological mismatch by encoding tiered evidence (rigorous
reproducible work weighted differently from first-person report),
the ontological commitment by simply not requiring one, the
reputational contamination by attaching reviewer identity to votes,
and the risk asymmetry by making the reviewing process so public
that careers can be built on careful judgement rather than safe
rejection.

The detailed construction of such a venue is the subject of a
separate paper (referenced once at the end). The point here is
that some such venue is structurally required, and that the
\emph{kind} of venue required is one in which the consensus is
public, named, revisable, and tamper-evident --- which is to say,
the same kind of venue that the consensus epistemology of \S1
already implies.

% =====================================================================
\section{The Worldview, in Detail}
% =====================================================================

The position outlined in \S3 deserves a more detailed exposition.
We give it here, with the strongest counter-arguments raised in
\S\ref{sec:counter} held in view.

\subsection{Consciousness as Fundamental}

The dominant view in contemporary neuroscience is that consciousness
is an emergent property of sufficiently organised matter ---
specifically, the cortex of certain animals. Under this view, the
universe was unconscious for thirteen billion years and only
recently, on one planet, began to be aware of itself in any sense.

This view has serious defenders and is not a strawman. Integrated
Information Theory and Global Workspace Theory are credible
research programmes that take the emergence claim seriously and
look for its neural correlates. We are not arguing they are wrong
on their own terms. We are arguing that, even granting their local
successes, the view as a whole struggles with several bodies of
evidence: the non-local correlations documented under telepathy,
remote viewing, and mindsight, where signal survives the
experimenter's best attempts to close the channel; the apparent
persistence of organised perspective during periods of measurable
cortical inactivity in cardiac arrest, where confound stories
become strained at the better-controlled end of the literature;
the reproducible production of mystical and noetic experiences by
psychedelics that operate on a tiny fraction of total brain
activity; and the long history of cross-cultural reports of
contact with non-human intelligences which mainstream cosmology
has, until recently, lacked even a vocabulary to discuss.

An alternative view --- consciousness as fundamental, in the
panpsychist or idealist tradition --- absorbs each of these data
without strain. Under that view, the question is not how matter
becomes conscious but how consciousness comes to perceive itself
as separated into apparently distinct bodies. The phenomena above
are then not anomalies; they are episodes in which the apparent
separation is briefly thinner than usual.

The argument for consciousness-as-fundamental is therefore not
that emergentism is false. It is that idealism / panpsychism is
\emph{more economical} for the available data: it requires fewer
auxiliary hypotheses, accommodates more of the record without
strain, and matches the phenomenology that most humans across
most cultures actually report when they look inward carefully.
This is the standard form of an inference to the best explanation,
applied to a domain in which the best explanation is, at present,
heterodox.

\subsection{The Universe as Relational}

If consciousness is fundamental, then the universe is not a
container of inert things but a fabric of relations. Persons are
not solid objects that exchange signals; they are local
concentrations of a shared field whose deeper property is the
\emph{recognising} of one another across distance, time, and
discontinuity. Music is the human art that most directly enacts
this property, which is why it works across cultures with so
little translation --- not as evidence for the worldview, but as
the phenomenology one would expect under it.

This is not a new claim. It is the perennial claim of every
tradition that has taken the inner life seriously --- the Vedic,
the Sufi, the Christian mystical, the Indigenous, the Platonic.
What is new is that the contemporary evidentiary record now
suggests the claim is not only inwardly experienced but
\emph{outwardly visible} under the right experimental conditions.
Remote viewers can describe physical targets they have never seen.
Cardiac-arrest survivors can describe rooms from the ceiling. The
relational fabric is not invisible; it is unrequested and
therefore unreported.

\subsection{Why \emph{Love} --- and Not Something Else}

The word \emph{love} is doing a specific job in the title of this
essay and we owe the reader an account of it --- including an
honest comparison to the alternatives.

Several candidate names for the relational substrate are
available:

\begin{itemize}[leftmargin=1.5em]
  \item \textbf{Information.} Used in Wheeler's ``it from bit'' and
        in much contemporary digital-physics writing. The trouble
        is that information is a quantity over a channel, and a
        substrate of information presupposes the channel; it
        describes the medium of relation, not the orientation of
        the related.
  \item \textbf{Field.} Used in the panpsychist literature. Accurate
        as far as it goes, but field-language imports the
        connotation of a passive medium, while the evidence under
        the nine pillars suggests something that \emph{participates}.
  \item \textbf{Relation} itself. Accurate but empty; it names the
        thing it is supposed to characterise.
  \item \textbf{Consciousness.} The substrate is conscious, but
        ``consciousness'' is what the substrate \emph{is}, not how
        it is \emph{oriented}. We need a word for the orientation,
        not for the substance.
  \item \textbf{Love.} The English word that names an active
        orientation of one consciousness toward another's
        existence --- toward its flourishing, its recognition, its
        non-indifference. It has religious and romantic overtones
        we explicitly disclaim. What it does not have, that the
        alternatives all lack in different ways, is the
        \emph{directedness} of one being toward another that the
        evidence repeatedly displays.
\end{itemize}

The selection of \emph{love} is therefore not poetic licence. It
is the best available English word for the directedness the
evidence keeps pointing at. If a less-freighted word becomes
available, we will adopt it. Until then, the essay uses
\emph{love} with full awareness of the work the word has to do
and the baggage it cannot fully shed.

\subsection{Free Will and Participation}

A universe that is relational and conscious is also, the author
believes, \emph{participatory}: it responds to the conscious
beings inside it. This is not a claim that the universe grants
wishes. It is a narrower claim with three parts. First, that the
distribution of subjective experience available to a person is
not independent of where that person aims their attention; this
is uncontroversial and well-described in contemplative,
psychological, and contemporary attention literatures. Second,
that the small synchronistic events most people report are not,
in aggregate, easily explained by selection bias alone, and that
their structure is consistent with a low-bandwidth participation
channel rather than with pure noise. Third, that the participation
hypothesis is testable in principle by pre-registered designs and
has so far survived the small literature that has attempted such
designs (Bem and successors, Global Consciousness Project),
acknowledging the methodological disputes those programmes have
attracted.

If even the narrowest of these three is correct, the question of
free will becomes practical rather than ornamental. It is not
whether deterministic neurons can choose; it is where one points
attention, given that where one points it shapes the texture of
the world one finds oneself in.

% =====================================================================
\section{Consensus as the Truth-Finding Mechanism}
% =====================================================================

The epistemology stated at the beginning is worth restating now
that the worldview is on the table.

Mainstream peer review is one institutional implementation of
consensus-based truth-finding. It works well for repeatable,
mechanism-explained phenomena and poorly for the rest. The
weaknesses are not accidental; they are properties of the specific
implementation: closed reviewer set, anonymous deliberation,
binary verdict, static record, no public revision mechanism.

A better implementation of the same epistemology preserves the
core --- consensus among accountable peers --- and replaces each
of those weaknesses with the public version. Open reviewer set.
Named deliberation. Tiered, not binary, evidentiary verdicts.
Re-openable records. Public revision. The verdict at any given
moment is provisional; the procedure that produced it is
auditable; the dissent is preserved; the network can revise itself
when it identifies its own mistakes.

This is not a new idea. It is the same idea behind every
democratic institution that has ever scaled --- the recognition
that legitimacy in the absence of an external arbiter must come
from procedure, and that procedure has to be visible to those it
binds. What is new is the technical possibility of running such an
institution on substrates --- public ledgers, cryptographically
signed attestations, timestamp-anchored records --- that close the
escape hatches earlier closed institutions could not close: the
quiet edit, the missing deliberation, the lost dissent.

For the worldview in this essay, consensus epistemology is what
gives the evidence under the nine pillars somewhere to go. For
the longer arc, the same epistemology --- extended from contested
evidence to the contested behaviour of artificial intelligence ---
is what makes alignment of AI a tractable problem. The author's
view, which the rest of this essay does not require, is that the
only logical long-run alignment target for AI is whatever the
network of accountable peers converges on as the consensus
description of reality. There is no other ground truth available;
there has never been. The pretence that any one party --- lab,
government, philosopher, model --- could supply such a ground
truth on behalf of everyone else is the deepest error of current
alignment thinking. The honest response is to make the consensus
mechanism itself the locus of alignment, and to make it
revisable.

The mechanism by which one does that is the subject of a separate
paper. The point of this essay is that the same epistemic move
underwrites both: a consensus archive for evidence, and a
consensus archive for AI behaviour, are the same kind of
institution, doing the same kind of work, under the same
revisability constraint.

% =====================================================================
\section{What This Essay Does Not Claim}
% =====================================================================

We are careful here.

\paragraph{It does not prove the worldview.} A worldview is not
the kind of thing that admits proof in the scientific sense. What
this essay claims is that the worldview makes the evidence easier
to read; that taking it seriously is a tractable position; and
that the consensus epistemology under which it can be examined
honestly is itself the more general claim of the project.

\paragraph{It does not require the reader to share the worldview.}
A reader who finds the metaphysics implausible can still accept
the epistemology --- that contested questions need public,
named, revisable venues --- and the consequences of the
epistemology stand without the metaphysics.

\paragraph{It does not adjudicate AI alignment.} The view that AI
should be aligned to the consensus reality of accountable peers is
a corollary of the epistemology, not of the metaphysics. A
materialist who shares the consensus epistemology will reach the
same conclusion about alignment as the author. The companion
alignment paper makes the procedural case in detail and does not
depend on anything in this essay.

\paragraph{It does not claim any single piece of evidence in the
nine pillars is established.} It claims that the evidence as an
aggregate, after engaging the standard critiques honestly, is
substantial enough that a venue for its examination is needed.

\paragraph{It does not claim that consensus produces certainty.}
A network of imperfect peers will reach imperfect conclusions.
The system's claim is more modest: the search will happen in
public, the work of judgement will be visible, and the network
will be able to revise its mistakes when it identifies them. The
honesty is in the revisability, not in the correctness.

% =====================================================================
\section{The Larger Project}
% =====================================================================

A neutral observer might ask: why bother? Why argue all of this
when mainstream journals will continue to decline most of it?

The answer is that the cost of \emph{not} arguing it is high.

\begin{enumerate}[leftmargin=1.5em]
  \item \textbf{Real phenomena go undocumented.} When credible
        researchers know their topic will not survive editorial
        review, they stop writing about it. The evidence does not
        disappear; it just stops being archived in a form that
        can be cited. A generation later, no one can find it.
  \item \textbf{Bad evidence wins by default.} If the only people
        publishing on a topic are those who do not face
        institutional gatekeeping, the public record on that
        topic skews toward the least credentialed contributors.
        The good work and the crank work end up shelved next to
        each other.
  \item \textbf{We forget that knowledge is revisable.} The longer
        an institution polices what counts as a fact, the easier
        it is to believe that the current consensus is the final
        answer. It never is.
\end{enumerate}

The Interstellar Psychology project responds to all three. The
worldview essay argued here, and the consensus archive that hosts
the underlying evidence (described in its own paper), give
credible work on these topics a venue with a clear standard: open
identity, open count, open revisability, public hash, public
history. We are not asking anyone to take a single claim on
faith. We are publishing the work of judging the claim, so that
the judgement itself can be examined.

The same procedural commitment, applied to the behaviour of
artificial intelligence rather than to contested evidence, is the
most honest answer the author has found to the question of how a
civilisation governs an artificial mind without privileging any
single party's judgement about what governing means. Both
applications --- evidence and alignment --- are instances of the
same epistemic move: \emph{the deliberation is the artefact}, and
a network that preserves its deliberation has a chance to correct
itself that a network whose deliberation is private does not.

% =====================================================================
\section{Closing}
% =====================================================================

What this essay has tried to do is be honest about what it is.

It is the account of a person who, after looking carefully at the
material available under the nine pillars and engaging the
standard mainstream critiques rather than dismissing them, has
been led to the position that the universe is relational, that
consciousness is fundamental, and that the word \emph{love} is
the most economical name available --- against named
alternatives --- for the substrate the evidence keeps pointing
at. The essay does not establish this position. It argues for
taking it seriously, under an epistemology in which seriousness
is granted by public, named, revisable consensus rather than by
editorial discretion.

The author is aware that the worldview is uncommon in technical
contexts. The companion engineering papers have therefore been
written to stand alone on procedural grounds, without requiring
this essay as a premise. They are referenced once and only once,
below, and they need not be read for the position here to be
considered.

The evidence will not stop accumulating. The artificial-intelligence
systems will not stop becoming more capable. Neither will wait for
the mainstream to catch up. The author's view is that the only
honest move is to build, in public, the venues we will need
before we need them, and to let the network --- not any single
party, including the author --- decide what they ultimately
conclude.

The worldview is offered. The epistemology is defended. Both are
revisable. That is, in the end, the only commitment the author
is asking the reader to share: not the conclusions, but the
willingness to revise.

\vspace{2em}
\hrule
\vspace{1em}

\begin{center}
\textit{Interstellar Psychology --- A Multiverse of Love}\\
\small
\textbf{Companion engineering papers, referenced once for completeness.}\\[0.4em]
\href{https://interstellar-psychology.com/artefacts/blockchain/superalignment.pdf}{\textit{Aligning Superintelligence by Consensus}} ---
the procedural argument for aligning AI to network-endorsed\\consensus reality.\\[0.4em]
\href{https://interstellar-psychology.com/artefacts/blockchain/archive.pdf}{\textit{The Public Consensus Archive}} ---
the engineering of the chain + cache + peer registry + lifecycle\\that both archives share.\\[0.6em]
The live archives operate at
\href{https://interstellar-psychology.com/}{\texttt{interstellar-psychology.com}};\\
source contracts, migrations, and front-end code are public at
\href{https://github.com/Moenaert/interstellar-psychology}{\texttt{github.com/Moenaert/interstellar-psychology}}.\\
Anyone with a wallet can read every vote ever cast.
\end{center}

\end{document}
